Multi-level music structure analysis: an audio-based approach using deep learning

### 2023-02-06 introduction/introduction.tex
Updates from Overleaf

As a music lover and connoisseur, I am interested in gaining a deeper understanding of the fundamental building of musical composition and the various techniques used to create musical works~\cite{choi2017convolutional}. I am deeply interested in learning how to retrieve embedded and encoded information within the music. The study of music structure analysis provides a means to systematically analyze and understand musical pieces. It has traditionally been approached through music theory, formal musical notation, musical analysis techniques, and machine learning, which I plan to blend.

@@

In previous work, an overview of the current state of the art in MSA has been presented, including the most effective methods, principles, evaluation metrics, datasets, and algorithm performance~\cite{Nieto2020}~\cite{Chaki2021}.

As a professional music transcriber, I aim to understand how deep neural networks (DNNs) filter musical features, listen to the NN layers from a musician's perspective and analyze the resulting data. My goal is to approach the technology from both a technical and musical standpoint to understand how DNNs process and extract musical information. By doing so, you aim to enhance the accuracy and efficiency of the process and contribute to developing AI technology for music analysis. By combining my expertise in music with my -not fully developed- knowledge of DNNs, I hope to bring a unique perspective to the field and contribute to the advancement of music analysis.

>>>>

As a music lover and connoisseur, I am interested in gaining a deeper understanding of the fundamental building of musical composition and the various techniques used to create musical works. I am deeply interested in learning how to retrieve embedded and encoded information within the music. The study of music structure analysis provides a means to systematically analyze and understand musical pieces. It has traditionally been approached through music theory, formal musical notation, musical analysis techniques, and machine learning, which I plan to blend.

@@

As a professional music transcriber, I aim to understand how deep neural networks (DNNs) filter musical features, listen to the NN layers from a musician's perspective and analyze the resulting data. I aim to approach the technology from a technical and musical standpoint to understand how DNNs process and extract musical information. By doing so, I aim to enhance the accuracy and efficiency of the process and contribute to developing AI technology for music analysis. By combining my expertise in music with my -not fully developed- knowledge of DNNs, I hope to bring a unique perspective to the field and contribute to the advancement of music analysis.

### 2023-02-06 music analysis/authors.tex
Updates from Overleaf

\section{The music structure analysis problem}
Audio-based Music Structural Analysis (MSA) identifies adjacent and non-overlapping musical segments in an audio signal and labels them based on similarity. Segments can occur at various time scales, from short motives to longer sections. Flat MSA focuses on non-hierarchical structures, while hierarchical MSA considers multiple time scales. However, MSA faces challenges such as boundary placement ambiguity and similarity quantification. Segments must be non-overlapping for a given hierarchical level, although some musicological approaches allow for overlap.

@@

As an art form, music is open to interpretation and can evoke different emotions and meanings in different listeners. This subjectivity makes it difficult to objectively analyze the structure of a piece of music, as different annotators may place boundaries between segments differently based on their perception and interpretation of the music. It can also have multiple structures, including hierarchical structures that make it difficult to untangle the truth.

@@

\section{Theoretical approach}
\subsection{Heinrich Schenker}

>>>>

~\cite{Nieto2020}~\cite{Chaki2021}

\section{The music structure analysis problem}

Audio-based Music Structural Analysis (MSA) identifies adjacent and non-overlapping musical segments in an audio signal and labels them based on similarity. Segments can occur at various time scales, from short motives to longer sections. Flat MSA focuses on non-hierarchical structures, while hierarchical MSA considers multiple time scales. However, MSA faces challenges such as boundary placement ambiguity and similarity quantification. Segments must be non-overlapping for a given hierarchical level, although some musicological approaches allow for overlap.

@@

As an art form, music is open to interpretation and can evoke different emotions and meanings in different listeners. This subjectivity makes it difficult to objectively analyze the structure of a piece of music, as different annotators may place boundaries between segments differently based on their perception and interpretation of the music. It can also have multiple structures, including hierarchical structures, that make it difficult to untangle the truth.

@@

\section{Theoretical approach}
\subsection{Music form}

Music form refers to the structural organization of a musical composition or performance. This can include elements such as the arrangement of musical units (such as rhythm, melody, and harmony) that exhibit repetition or variation, the arrangement of instruments, or the orchestration of a symphonic piece. These elements interact to shape the composition and create a meaningful musical experience for the listener. The organizational elements can be further broken down into smaller units called phrases, which express a musical idea but lack sufficient weight to stand alone. The form of a composition unfolds over time through the expansion and development of these ideas. In tonal harmony, form is primarily articulated through cadences, phrases, and periods.

\subsection{Heinrich Schenker}

### 2023-02-06 music analysis/music structure analysis.tex
Updates from Overleaf

In Schenkerian analysis, the fundamental structure, also known as Ursatz, represents the underlying structure of a tonal work at the most remote or background level, in the most abstract form. It comprises an essential elaboration of the tonic triad, including the entire line and accompanying bass arpeggiation. The fundamental structure, like the fundamental line, takes one of three forms, depending on which pitch of the tonic triad serves as the primary tone. For example, in the key of C major, the fundamental structure would be represented by the fundamental descending line from scale degree 3.

@@

\section{Music form}

Music form refers to the structural organization of a musical composition or performance. This can include elements such as the arrangement of musical units (such as rhythm, melody, and harmony) that exhibit repetition or variation, the arrangement of instruments, or the orchestration of a symphonic piece. These elements interact to shape the composition and create a meaningful musical experience for the listener. The organizational elements can be further broken down into smaller units called phrases, which express a musical idea but lack sufficient weight to stand alone. The form of a composition unfolds over time through the expansion and development of these ideas. In tonal harmony, form is primarily articulated through cadences, phrases, and periods.

>>>>

In Schenkerian analysis, the fundamental structure, also known as Ursatz, represents the underlying structure of a tonal work at the most remote or background level, in the most abstract form. It comprises an essential elaboration of the tonic triad, including the entire line and accompanying bass arpeggiation. The fundamental structure, like the fundamental line, takes one of three forms, depending on which pitch of the tonic triad serves as the primary tone. For example, the key of C major would represent the fundamental structure by the fundamental descending line from scale degree 3.

@@

### 2023-02-06 results/results.tex
Updates from Overleaf

>>>>

There is no stringent page limit. The size and the total number of your figures and tables will strongly influence your number of pages. It is recommended to stay within 30-50 pages. Do not try to fill as many pages as you can. Longer theses are not necessarily of higher quality and have more non-redundant content than shorter theses. Indeed, a master thesis of 15 pages is too short, and a master thesis of 100 pages is too long.
